Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-01-25 Master Thesis/synopsis.tex
Complete symbols

We denote the valuation ring of $v\in\operatorname{Spv}(K)$ by $(\mathcal{O}_v,\mathfrak{m}_v)$ and set $U_v=\mathcal{O}_v^\times$ and $k(v)=\mathcal{O}_v/\mathfrak{m}_v$. The \textit{rank}\index{valuation!rank} of $v$ is defined as the Krull dimension of its valuation ring $\mathcal{O}_v$. The \textit{rational rank}\index{valuation!rational rank} of $v:K^\times\to\Gamma_v$ is defined as the rank of its valuation group $\Gamma_v$ as a $\mathbb{Z}$-module:
\[\operatorname{rrank}(v) = \dim_\mathbb{Q}(\Gamma_v\otimes_\mathbb{Z}\mathbb{Q}) \]
\end{definition}

@@

\begin{definition}
We define:
\begin{align*}
\operatorname{Spv}_\text{d}(K) &= \{v\in\operatorname{Spv}(K)\mid\operatorname{rank}(v)=\operatorname{rrank}(v) \} \\
\operatorname{Spv}_\text{rd}(K) &= \{v\in\operatorname{Spv}_\text{d}(K)\mid \operatorname{rrank}(v)+\dim k(v)=\dim(K) \}
\end{align*}
Valuations in $\operatorname{Spv}_\text{d}$ are called \textit{defectless}\index{valuation!defectless}, whereas those in $\operatorname{Spv}_\text{rd}$ are called \textit{rank-defectless}\index{valuation!rank-defectless}. For $\ast\in\{\text{d},\text{rd}\}$ we set:
\[\operatorname{Spv}_\ast^{(i)}(K)=\{v\in\operatorname{Spv}_\ast(K)\mid \operatorname{rrank}(v)=i \} \]
\end{definition}

>>>>

We denote the valuation ring of $v\in\operatorname{Spv}(K)$ by $(\mathcal{O}_v,\mathfrak{m}_v)$ and set $U_v=\mathcal{O}_v^\times$ and $k(v)=\mathcal{O}_v/\mathfrak{m}_v$. The \textit{rank}\index{valuation!rank} of $v$ is defined as the Krull dimension of its valuation ring $\mathcal{O}_v$. The \textit{rational rank}\index{valuation!rational rank} of $v:K\to\Gamma_v\cup\{\infty\}$ is defined as the rank of its valuation group $\Gamma_v$ as a $\mathbb{Z}$-module:
\[\operatorname{rrank}(v) = \dim_\mathbb{Q}(\Gamma_v\otimes_\mathbb{Z}\mathbb{Q}) \]
\end{definition}

@@

\begin{definition}
We define:
\begin{align*}
\operatorname{Spv}_\text{d}(K) &= \{v\in\operatorname{Spv}(K)\mid\operatorname{rank}(v)=\operatorname{rrank}(v) \} \\
\operatorname{Spv}_\text{rd}(K) &= \{v\in\operatorname{Spv}_\text{d}(K)\mid \operatorname{rrank}(v)+\dim k(v)=\dim(K) \}
\end{align*}
Valuations in $\operatorname{Spv}_\text{d}(K)$ are called \textit{defectless}\index{valuation!defectless}, whereas those in $\operatorname{Spv}_\text{rd}(K)$ are called \textit{rank-defectless}\index{valuation!rank-defectless}. For $\ast\in\{\text{d},\text{rd}\}$ we set:
\[\operatorname{Spv}_\ast^{(i)}(K)=\{v\in\operatorname{Spv}_\ast(K)\mid \operatorname{rrank}(v)=i \} \]
\end{definition}
